---
title: "Chicago Transit Deserts - Summary"
author: "Zack Woods"
date: "5/8/2022"
output: html_document
---

## Environment Setup 

```{r}
setwd("~/Desktop/chiTransitDesertsProj")
library(sf)
library(tmap)
library(dplyr)
```

## Load datasets

> Chicago census tracts, bus & train routes/stops, street networks, bike routes, sidewalks

```{r}
chiTracts <- read_sf("tracts_26971.shp")
railLines <- read_sf("railLines/CTA_RailLines.shp")
busLines <- read_sf("busRoutes/CTA_BusRoutes.shp")
bikeRoutes <- read_sf("bikeRoutes/geo_export_d5b2a8a7-f33d-4a3b-ac07-ec016dc1088b.shp")
busStops <- read_sf("busStops/CTA_BusStops.shp")
railStops <- read_sf("railStops/CTA_RailStations.shp")
bikeRoutes <- read_sf("bikeRoutes/geo_export_d5b2a8a7-f33d-4a3b-ac07-ec016dc1088b.shp")
chiRoads <- read_sf("chiRoads/geo_export_6c7ad2b5-cc81-4e18-a45b-471d70ced40f.shp")
il_bounds <- read_sf("IL_BNDY_State/IL_BNDY_State_Ln.shp")
```

## Map variables

> Overlay each route/variable on a map of Chicago - bus routes, train routes, bus stops, train stops, roads, bike routes, sidewalks


```{r}
tm_shape(chiTracts) + tm_fill() + tm_borders()
tm_shape(chiTracts) + tm_fill() + tm_shape(railLines) + tm_lines()
tm_shape(chiTracts) + tm_fill() + tm_shape(busLines) + tm_lines()
tm_shape(chiTracts) + tm_fill() + tm_shape(bikeRoutes) + tm_lines()
tm_shape(chiTracts) + tm_fill() + tm_shape(chiRoads) + tm_lines()
tm_shape(chiTracts) + tm_fill() + tm_shape(busStops) + tm_dots()
tm_shape(chiTracts) + tm_fill() + tm_shape(railStops) + tm_dots()
```

## Create choropleth maps of each variable

>Variables of interest: # of transit stops, service frequency, # of transit routes, sidewalk length, bike route length, intersection density

```{r}
tm_shape(chiTracts) + tm_fill("bikeLength", style = "jenks", palette = "BuPu", legend.hist = TRUE) + tm_borders(alpha = 0.05) + tm_layout(legend.outside = TRUE)
tm_shape(chiTracts) + tm_fill("numRoutes", style = "jenks", palette = "BuPu", legend.hist = TRUE) + tm_borders(alpha = 0.05) + tm_layout(legend.outside = TRUE)
tm_shape(chiTracts) + tm_fill("roadLength", style = "jenks", palette = "BuPu", legend.hist = TRUE) + tm_borders(alpha = 0.05) + tm_layout(legend.outside = TRUE)
tm_shape(chiTracts) + tm_fill("transitSto", style = "jenks", palette = "BuPu", legend.hist = TRUE) + tm_borders(alpha = 0.05) + tm_layout(legend.outside = TRUE)

```

## Cluster analysis

```{r}

```

